Papers

### 2024-07-27 quarto/index.qmd
update

* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. Check out <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Mark's insights</a> on Llama 3 and beyond. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Join us for a 2024 research internship (filled, see you next time). <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

@@

* Llama Team, AI@Meta (**Core Contributor**)<br>
<a href="https://scontent-sjc3-1.xx.fbcdn.net/v/t39.2365-6/452256780_3788187148167392_9020150332553839453_n.pdf?_nc_cat=103&ccb=1-7&_nc_sid=3c67a6&_nc_ohc=XG3_BvYG0wwQ7kNvgGBgyGR&_nc_ht=scontent-sjc3-1.xx&oh=00_AYDGOU8907donbx_n2EYOzFU-h4VJxtA_EjJbiFVm7qnaA&oe=66A5A0DC" target="_blank">The Llama 3 Herd of Models</a><br>
2024<br>
<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>

>>>>

* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. Explore <a href="https://x.com/rowancheung/status/1815763595197616155" target="_blank">Mark's insights</a> on Llama 3 and beyond. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Join us for a 2024 research internship (filled, see you next time). <a href="https://twitter.com/astonzhangAZ/status/1731698624902402281" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

@@

* Llama Team, AI@Meta (**Core Contributor**)<br>
<a href="https://ai.meta.com/research/publications/the-llama-3-herd-of-models/" target="_blank">The Llama 3 Herd of Models</a><br>
2024<br>
<a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
<a href="https://github.com/meta-llama/llama-models" title="Code" target="_blank"><img src="./img/logo-github.svg" class="paper-icon"></a>
